Create datasets for supplemental analyses

### 2023-03-21 code/maps.qmd
Revert to commit 04afdf914d146eb948b43412668012bbc116cd82.

```{r}
library(sf)
library(tmap)
library(stars)
library(grid)
library(readr)
```

## Map of exome capture sample sites

@@

>>>>

```{r}
library(sf)
library(tmap)
library(stars)
library(grid)
library(tidyverse)
library(RPostgreSQL)
```

## Map of sample sites for exome capture analysis

Run the following 4 chunks only if you have access to the project database. For those without the necessary credentials, use the saved output file in data/maps/ that is available via the "import-map-data1" chunk.

### Create dataset of sample collection points

```{r}
exome_sites <- read_csv(here::here("data", "maps", "exome_sample_sites.csv"))
```

#### Connect to database

```{r}
source("db_connect.R")
```

#### Retrieve data & create points layer

```{r}
n <- nrow(exome_sites)

exome_points <- dbReadTable(con, c("site")) %>% 
  as_tibble() %>% 
  rename(site_id = id) %>% 
  select(site_id, utme, utmn) %>% 
  inner_join(exome_sites, by = "site_id") %>% 
  add_column(x = sample(-2000:2000, size = n), # Add x-y random noise to obscure exact site locations
             y = sample(-2000:2000, size = n)) %>% 
  mutate(utme_noise = utme + x,
         utmn_noise = utmn + y) %>% 
  select(-utme, -utmn, -x, -y)

write_csv(exome_points, here::here("data", "maps", "exome_points.csv"))
```

#### Disconnect from database

```{r}
source("db_disconnect.R")
```

@@

Run the following 4 chunks only if you have access to the project database. For those without the necessary credentials, use the saved output file in data/maps/ that is available via the "import-map-data2" chunk.

### Create dataset of site points

```{r}
donor_sites <- read_csv(here::here("data", "clean", "frog_translocation_final.csv")) %>% 
  distinct(donor) %>% 
  mutate(site_id = donor, .before = donor) %>% 
  rename(donor_id = donor) %>% 
  add_column(type = "donor")

translocation_sites <- read_csv(here::here("data", "clean", "frog_translocation_final.csv")) %>% 
  distinct(site_id, donor) %>% 
  rename(donor_id = donor) %>% 
  add_column(type = "translocation") %>% 
  bind_rows(donor_sites)

rm(donor_sites)
```

#### Connect to database

```{r}
source("db_connect.R")
```

#### Retrieve data & create points layer

```{r}
n <- nrow(translocation_sites)

translocation_points <- dbReadTable(con, c("site")) %>% 
  as_tibble() %>% 
  rename(site_id = id) %>% 
  select(site_id, utme, utmn) %>% 
  inner_join(translocation_sites, by = "site_id") %>% 
  add_column(x = sample(-2000:2000, size = n), # Add x-y random noise to obscure exact site locations
             y = sample(-2000:2000, size = n)) %>% 
  mutate(utme_noise = utme + x,
         utmn_noise = utmn + y) %>% 
  select(-utme, -utmn, -x, -y)

write_csv(translocation_points, here::here("data", "maps", "translocation_points.csv"))
```

#### Disconnect from database

```{r}
source("db_disconnect.R")
```

### 2023-03-21 code/translocation_survival_createdata_supp.Rmd
Revert to commit 04afdf914d146eb948b43412668012bbc116cd82.

-   Users without credentials to access the database can utilize .csv files saved below when running code in the `translocation_survival_supp.Rmd` and `maps.qmd` files.

@@

## DATASETS 3: Create datasets for study site maps

### Map of sample sites for exome capture analysis

#### Create dataset of sample collection points

```{r}
exome_sites <- read_csv(here::here("data", "maps", "exome_sample_sites.csv"))
```

#### Retrieve data from database & create points layer

```{r}
source("db_connect.R")

n <- nrow(exome_sites)

exome_points <- dbReadTable(con, c("site")) %>% 
  as_tibble() %>% 
  rename(site_id = id) %>% 
  select(site_id, utme, utmn) %>% 
  inner_join(exome_sites, by = "site_id") %>% 
  add_column(x = sample(-2000:2000, size = n), # Add x-y random noise to obscure exact site locations
             y = sample(-2000:2000, size = n)) %>% 
  mutate(utme_noise = utme + x,
         utmn_noise = utmn + y) %>% 
  select(-utme, -utmn, -x, -y)

source("db_disconnect.R")

write_csv(exome_points, here::here("data", "maps", "exome_points.csv"))
```

### Map of Yosemite translocation & donor sites

#### Create dataset of site points

```{r}
donor_sites <- read_csv(here::here("data", "clean", "frog_translocation_final.csv")) %>% 
  distinct(donor) %>% 
  mutate(site_id = donor, .before = donor) %>% 
  rename(donor_id = donor) %>% 
  add_column(type = "donor")

translocation_sites <- read_csv(here::here("data", "clean", "frog_translocation_final.csv")) %>% 
  distinct(site_id, donor) %>% 
  rename(donor_id = donor) %>% 
  add_column(type = "translocation") %>% 
  bind_rows(donor_sites)

rm(donor_sites)
```

#### Retrieve data from database & create points layer

```{r}
source("db_connect.R")

n <- nrow(translocation_sites)

translocation_points <- dbReadTable(con, c("site")) %>% 
  as_tibble() %>% 
  rename(site_id = id) %>% 
  select(site_id, utme, utmn) %>% 
  inner_join(translocation_sites, by = "site_id") %>% 
  add_column(x = sample(-2000:2000, size = n), # Add x-y random noise to obscure exact site locations
             y = sample(-2000:2000, size = n)) %>% 
  mutate(utme_noise = utme + x,
         utmn_noise = utmn + y) %>% 
  select(-utme, -utmn, -x, -y)

source("db_disconnect.R")

write_csv(translocation_points, here::here("data", "maps", "translocation_points.csv"))
```

>>>>

-   Users without credentials to access database can utilize `subadult_survival.csv` and `tadpole_survival.csv` saved below.

@@
